---
title: "p8105_hw1_yq2251"
author: "TritonD"
date: "9/13/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Question 1
## create data frame

```{r}
library(tidyverse)

hw1_df=tibble(
   vec_numeric=rnorm(n=8, mean=0, sd=1),
   vec_logical=vec_numeric>0,
   vec_char=c("This", "is", "my", "first", "class", "using", "R", "code"),
   vec_factor=factor(c( "a","a","b","b","c","c","c","c"))
)
```

#take mean of each variable
```{r}
mean(pull(hw1_df, vec_numeric))
mean(pull(hw1_df, vec_logical))
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, vec_factor))
```
#the numeric and logical vectors have the mean, the others don't.

##write a chunk to convert logical, character, and factor variables into numeric
```{r}
as.numeric(pull(hw1_df, vec_logical))
as.numeric(pull(hw1_df, vec_char))
as.numeric(pull(hw1_df, vec_factor))
```
#According to the output,logical vector can be converted to numeric vector with "true" or "false" replaced by "1" and "0".
#Both character and factor vectors failed to be converted to numeric vector with a "NA" result.
#Mean function is specifically for numeric values, thie explained why only numeric and logical vectors have the mean

#write a second chunk to convert logical vector with extra sample calculation
```{r}
pull(hw1_df, vec_numeric)*as.numeric(pull(hw1_df, vec_logical))
pull(hw1_df, vec_numeric)*as.factor(pull(hw1_df, vec_logical))
as.numeric(as.factor(pull(hw1_df, vec_logical)))*pull(hw1_df, vec_numeric)
```

##Question 2
## create data frame
```{r}
hw1_df2=tibble(
   x=rnorm(n=500, mean=0, sd=1),
   y=rnorm(n=500, mean=0, sd=1),
   vec_logical=x+y>1,
   vec_numeric=as.numeric(vec_logical),
   vec_factor=as.factor(vec_logical)
)
```

#add inline R code to explain the dataset and results
The number of rows in dataset is `r nrow(hw1_df2)` rows and `r ncol(hw1_df2)` columns.
The mean of x is `r mean(pull(hw1_df2, x))`.
The median of x is `r median(pull(hw1_df2, x))`.
The standard deviation of x is `r sd(pull(hw1_df2, x))`.

The proportion of cases for which x + y > 1 is `r mean(pull(hw1_df2, vec_logical))`.

#draw scatterplot y versus x using logical variables
```{r}
ggplot(hw1_df2,aes(x=x,y=y,color=vec_logical))+geom_point()
```

#save the first scatterplot in the project directory
```{r}
ggsave("Rplot.png",width = 20, height = 20, units = "cm")
```

#draw scatterplot y versus x using numeric variables
```{r}
ggplot(hw1_df2,aes(x=x,y=y,color=vec_numeric))+geom_point()
```

#draw scatterplot y versus x using factor variables
```{r}
ggplot(hw1_df2,aes(x=x,y=y,color=vec_factor))+geom_point()
```







